---
title: "Wine Barrel Wall"
author: "Jason Taylor"
date: "`r Sys.Date()`"
output: 
  rmdformats::readthedown:
    self_contained: true
    thumbnails: false
    lightbox: true
    gallery: true
    highlight: NULL
    includes:
     after_body: footer.html
  html_document: 
    fig_caption: yes
    fig_height: 6
    fig_width: 8
    highlight: tango
editor_options: 
  chunk_output_type: console
---
Creating a radius wall for our new wine cellar. Using rstats to randomize the placement and color of the slats.

```{r libraries, include = FALSE, message = FALSE, results = FALSE}
library.list <- c("tidyverse", "ggtextures")
lapply(library.list, require, character.only = TRUE)
```

```{r}
set.seed(42)
width_board <- 2.5
width_int <- 89.5
width_ext <- 112
height <- 108

num_boards_int <- round(width_int / width_board, digits = 0)
num_boards_ext <- round(width_ext / width_board, digits = 0)
```

## Interior Wall Dimensions:

* Wall length `r width_int`"
* Wall height `r height`"
* Slats were cut to a width of `r width_board`" and are (36", 48", or 60" in length)


## Interior Wall Layout

```{r interior_wall}
slat <- sort(rep(1:num_boards_int, 3))
position <- rep(c("bottom", "middle", "top"), num_boards_int / 3)
len <- rep(c(3, 3, 3, 4, 5, NA, 5, 4, NA), num_boards_int / 3)

layout <- data.frame(cbind(slat, position, len),
                     stringsAsFactors = FALSE) %>%
  mutate(slat = as.numeric(slat), 
         len = as.numeric(len)) %>%
  filter(complete.cases(.))

layout$stain <- as.character(sample(1:2, size = nrow(layout), replace = TRUE))

layout <- mutate(layout, image_file = case_when(stain == "1" ~ "walnut.png",
                                                TRUE ~ "espresso.png"))

ggplot(layout, aes(x = slat, y = len, image = image_file, group = position)) +
  ggtextures::geom_textured_col(width = 1) + 
  scale_y_continuous(breaks = seq(0, 9, 3),
                     labels = scales::dollar_format(suffix = "ft", prefix = "")) +
  scale_x_continuous(breaks = seq(0, num_boards_int, 6)) +
  labs(x = "Slat Position", y = "Wall Position") +
  theme_bw() + 
  theme(plot.title = element_text(hjust = 0.5, size = 14,
                                  family = "Tahoma", face = "bold"),
        text = element_text(family = "Tahoma"),
        axis.text.x = element_text(colour = "black", size = 10),
        axis.text.y = element_text(colour = "black", size = 10)) +
  ggtitle("Wine Room Interior Wall")
```

## Exterior Wall Dimensions:

* Wall length `r width_ext`"
* Wall height `r height`"
* Slats were cut to a width of `r width_board`" and are (36", 48", or 60" in length)


## Exterior Wall Layout

```{r exterior_wall}
slat <- sort(rep(1:num_boards_ext, 3))
position <- rep(c("bottom", "middle", "top"), num_boards_ext / 3)
len <- rep(c(3, 3, 3, 4, 5, NA, 5, 4, NA), num_boards_ext / 3)

layout <- data.frame(cbind(slat, position, len), stringsAsFactors = FALSE) %>%
  mutate(slat = as.numeric(slat), 
         len = as.numeric(len)) %>%
  filter(complete.cases(.))

layout$stain <- as.character(sample(1:2, size = nrow(layout), replace = TRUE))

layout <- mutate(layout, image_file = case_when(stain == "1" ~ "walnut.png",
                                                TRUE ~ "espresso.png"))

ggplot(layout, aes(x = slat, y = len, image = image_file, group = position)) +
  ggtextures::geom_textured_col(width = 1) + 
  scale_y_continuous(breaks = seq(0, 9, 3),
                     labels = scales::dollar_format(suffix = "ft", prefix = "")) +
  scale_x_continuous(breaks = seq(0, num_boards_ext, 6)) +
  labs(x = "Slat Position", y = "Wall Position") +
  theme_bw() + 
  theme(plot.title = element_text(hjust = 0.5, size = 14,
                                  family = "Tahoma", face = "bold"),
        text = element_text(family = "Tahoma"),
        axis.text.x = element_text(colour = "black", size = 10),
        axis.text.y = element_text(colour = "black", size = 10)) +
  ggtitle("Wine Room Exterior Wall")
```